Performance Evaluation of Neural Networks for Intrusion Prevention Systems

### 2020-07-12 paper2/paper2.tex

It is expectable that there are differences in the intrusion detection datasets because, for example, cyber attacks are not always executed or recorded in the same way or the network infrastructure is structured differently. The aim is to determine how sensitive neural networks react to this and are thus dependent on the data with which they have been trained. This chapter is designed in such a way that the various steps for building up the neural network are first described and then the results obtained are examined in detail.

@@

\section{Conclusion}\label{conclusion}
In summary, the performance of neural networks in terms of intrusion detection over different datasets is rather mixed. If these machine learning algorithms are tested with the same dataset with which they were trained, the result is promising. Using another dataset for testing results in a poor classification performance. However, there is lots of potential for future research with neural networks in terms of intrusion detection. It seems useful to analyse in detail why the mentioned difficulties occur in the classification and which factors are relevant for the neural network. An intensive examination of the finding of optimal hyperparameters would also be desirable in the course of future work. Furthermore, it would also make sense to simplify the way classification is done. Instead, a simple classification like network traffic is “benign” or “not benign” would be conceivable. Moreover, it should be checked whether a better performance can be achieved with other machine learning algorithms.

>>>>

It is expectable that there are differences in intrusion detection or -prevention datasets because, for example, cyber attacks are not always executed or recorded in the same way or the network infrastructure is structured differently. The aim is to determine how sensitive neural networks react to this and are thus dependent on the data with which they have been trained. This chapter is designed in such a way that the various steps for building up the neural network are first described and then the results obtained are examined in detail.

@@

\section{Conclusion}\label{conclusion}
In summary, the performance of neural networks in terms of intrusion prevention over different datasets is rather mixed. If these machine learning algorithms are tested with the same dataset with which they were trained, the result is promising. Using another dataset for testing results in a poor classification performance. However, there is lots of potential for future research with neural networks in this context. It seems useful to analyse in detail why the mentioned difficulties occur in the classification and which factors are relevant for the neural network. An intensive examination of the finding of optimal hyperparameters would also be desirable in the course of future work. Furthermore, it would also make sense to simplify the way classification is done. Instead, a simple classification like network traffic is “benign” or “not benign” would be conceivable. Moreover, it should be checked whether a better performance can be achieved with other machine learning algorithms.
